sensi_an_rotations1 : start of sensitivity analysis for rotations

### 2018-01-08 inst/documents/sensi_an_rotations1.Rmd
struggling with dplyr

  # summarise results per scenario
  res <- dfres %>%
  dplyr::filter(active_or_refuge=='active') %>%
  group_by(resist_gene) %>%
  summarise(gens_under50 = sum(resistance < 0.5, na.rm=TRUE)) %>%
  summarise(mean_gens_under50 = mean(gens_under50)) %>%
  unlist()

>>>>

  # summarise results per scenario
  # NOTE this is also currently calc at end of run_rot() prob better to calc there
  # and put in the output dfres, but its then repeated per 
  # TODO first AG fix this maybe go for non dplyr solution
  # if I do calc in run_rot then just find value at first row for each gene
  # Error in dplyr::filter(active_or_refuge == "active") : 
  # object 'active_or_refuge' not found
  res <- dfres %>%
  # only assess in control areas not in refugia  
  dplyr::filter(active_or_refuge=='active') %>%
  group_by(resist_gene) %>%
  # for all insecticides in all generations  
  # summarise(gens_under50 = sum(resistance < 0.5, na.rm=TRUE)) %>%
  # summarise(mean_gens_under50 = mean(gens_under50)) %>%
  # just for deployed insecticides 
  summarise(gens_dep_under50 = sum(resistance < 0.5 &
                                   #finds insecticide in use = this one
                                   #TODO in_use is also calculated in rot_plots, but set to 1.05 for the plots
                                   resist_gene==paste0('insecticide',insecticide), na.rm=TRUE)) %>%
  summarise(tot_gens_dep_under50 = sum(gens_dep_under50)) %>%    
  unlist()
